%-------------------------
% Latex based Resume
% Author : Cloe Cha
% Based off of: https://github.com/jakegut/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

% serif
\usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\setlength{\footskip}{5pt}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%----------CUSTOM COMMANDS----------
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%----------------------------------------------------------
%--------------------RESUME STARTS HERE--------------------
%----------------------------------------------------------

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\huge Cloe Cha} \\ \vspace{2pt}
    \small (732) 915-6473 $|$ 
    \href{mailto:ccloecha@gmail.com}{ccloecha@gmail.com} $|$ 
    \href{https://www.linkedin.com/in/cloecha/}{linkedin.com/in/cloecha/} $|$ 
    \href{https://github.com/ccha3uw}{github.com/ccha3uw}
\end{center}

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Washington}{Seattle, WA}
      {Bachelor of Science in Human-Computer Interaction}{Sep 2022 -- Mar 2026}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Associate Product Manager}{Sep 2024 -- Oct 2025}
      {Vial Therapeutics}{San Francisco, CA (Remote)}
      \resumeItemListStart
        \resumeItem{Reduced protocol preparation time \textbf{75\%} by shipping an AI-powered document generator using Perplexity and Gemini that converts completed pre-clinical research into FDA-ready drafts, eliminating months of manual synthesis.}
        \resumeItem{Removed Engineering from the critical path by enabling non-technical teams to self-serve AI document generation through dynamic form logic and iterative editing workflows.}
        \resumeItem{Increased core product net promoter score from \textbf{17 to 82} over \textbf{12 months} by identifying recurring pain points through user research and delivering targeted workflow improvements.}
      \resumeItemListEnd

    \resumeSubheading
      {Product Management Intern}{May 2023 -- May 2024}
      {Vial Therapeutics}{San Francisco, CA (Remote)}
      \resumeItemListStart
        \resumeItem{Eliminated vendor dependency achieving a \textbf{97\%} cost reduction (\textbf{\$150K $\rightarrow$ \$5K/year}) by replacing a third-party e-signature vendor with an in-house solution embedded into core workflows.}
        \resumeItem{Delivered within \textbf{9 months} by establishing async planning, documentation, and execution processes that improved cross-functional delivery reliability and were adopted org-wide.}
        \resumeItem{Partnered with Legal and Compliance to translate regulatory requirements into technical specifications, enabling Engineering and UX to deliver a production-ready, FDA- and GDPR-compliant solution.}
      \resumeItemListEnd

    \resumeSubheading
      {Product Management Intern}{May 2024 -- Aug 2024}
      {Spring Health}{New York, NY (Remote)}
      \resumeItemListStart
        \resumeItem{Identified root causes of a \textbf{7\%} onboarding drop-off by pairing Mixpanel funnel analysis with \textbf{20} async Dscout interviews, informing product leadership decisions on onboarding flow changes.}
      \resumeItemListEnd

    \resumeSubheading
      {Product Management Intern}{May 2022 -- Aug 2022}
      {Eachday Health}{Pittsburgh, PA}
      \resumeItemListStart
        \resumeItem{Enabled a \textbf{\$325K} pre-seed raise (IndieBio) by delivering a validated MVP through Kanban workflows, weekly standups, and usability testing with \textbf{6 educators} and \textbf{18 students}.}
        \resumeItem{Validated core product assumptions by running accessibility and usability pilots at a special-needs school, informing MVP scope and de-risking the product for investors.}
      \resumeItemListEnd

    \resumeSubheading
      {Associate Student Researcher}{Jun 2022 -- Aug 2022}
      {Carnegie Mellon University, HCI Institute}{Pittsburgh, PA}
      \resumeItemListStart
        \resumeItem{Synthesized insights across \textbf{28 academic papers} by conducting a literature review analyzing core game design components and interaction patterns.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------LEADERSHIP-----------
\section{Leadership}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Capstone Team Lead}{Sep 2025 -- Dec 2025}
      {INFO 492 Intensive Capstone}{Seattle, WA}
      \resumeItemListStart
        \resumeItem{Led a 4-person team to build an agentic AI system for Puget Sound Energy, prototyping with v0 and implementing with Cursor + Ollama, automating audit record classification for substation operators.}
      \resumeItemListEnd

    \resumeSubheading
      {Selection Director}{Sep 2022 -- Mar 2023}
      {TEDxUofW}{Seattle, WA}
      \resumeItemListStart
        \resumeItem{Led 10-person student team to manage speaker selection across \textbf{150} nominated speakers.}
        \resumeItem{Collaborated with selected speakers to refine and finalize their speeches.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: JavaScript, Python, SQL, HTML/CSS, Java, Git} \\
     \textbf{Tools}{: Figma, Jira, PostHog, Mixpanel, Dscout, Excel, Tableau, Looker, Confluence, Intercom, V0, Cursor} \\
     \textbf{Skills}{: Product Discovery, PRDs, User Research, A/B Testing, Agile/SCRUM, Wireframing, Statistical Analysis}
    }}
 \end{itemize}

\end{document}